%!TEX root = ../Thesis.tex

% 6. Conclusion – or summing up?

% The final section of your thesis may take one of several different forms. Some theses need a conclusion, while for others a summing up will be appropriate. The decisive factor will be the nature of your thesis statement and/or research question.

% Open research questions cannot always be answered, but if a definite answer is possible, you must provide a conclusion. The conclusion should answer your research question(s). Remember that a negative conclusion is also valid.

% A summing up should repeat the most important issues raised in your thesis (particularly in the discussion), although preferably stated in a (slightly) different way. For example, you could frame the issues within a wider context.

% Placing your thesis in perspective

% In the final section you should place your work in a wider, academic perspective and determine any unresolved questions. During the work, you may have encountered new research questions and interesting literature which could have been followed up. At this point, you may point out these possible developments, while making it clear for the reader that they were beyond the framework of your current project.

% Briefly discuss your results from a different perspective. This will allow you to see aspects that were not apparent to you at the project preparation stage
% Highlight alternative research questions that you have found in the source materials used in the project
% Show how others have placed the subject area in a wider context
% If others have drawn different conclusions from yours, this will provide you with ideas of new ways to view the research question
% Describe any unanswered aspects of your project
% Specify potential follow up and new projects
% A thesis should “bite itself in the tail”

% There should be a strong connection between your conclusion and your introduction. All the themes and issues that you raised in your introduction must be referred to again in one way or another. If you find out at this stage that your thesis has not tackled an issue that you raised in the introduction, you should go back to the introduction and delete the reference to that issue. An elegant way to structure the text is to use the same textual figure or case in the beginning as well as in the end. When the figure returns in the final section, it will have taken on a new and richer meaning through the insights you have encountered, created in the process of writing.

\chapter{Conclusion}\label{total:chapters}
However short the time-frame was I managed to make a successful implementation which covers desired functionality, moreover supporting and supervising a few fellow teams. 

In the time span of a few months, we built a car only failing within battery connection. As we learnt from experience designing battery pack is an extremely time-consuming process especially when we take into consideration the safety constraints. Therefore in the following years, it is advised to greatly prioritise battery development in such way that it is the main element in the car and everything is built around it instead of trying to fit it in a final stage.

Although, failure of the battery associated team I did whatever I could to provide working main control unit and prove its functionality. Based on measurements I can claim that the system works as desired, however, I am really looking forward to finally see the car rolling and test empirically its performance on the track.

The car will be used for another half a year as a testing/development unit and the system has been well design for this purpose offering possibility to simulate each sub-module within a remote panel.

When it comes to future development first the most important improvement would be to use many redundant sensors for an electrical differential system. The current solution is really basic, for proper functioning in all condition I would recommend using additional encoders on non-driven wheels and acceleration/yaw sensor. Based on data obtained in this way one may accurately estimate vehicle state, considering accelerations, wheels spin and lateral slips. So elaborate traction assistance algorithms can be used.

%%%% Delete rest

The circumstances of the work on my thesis indirectly but forced me to work on a wide spectrum of tasks. Although interesting, it did not allow me to make these studies more in-depth on any particular part. 
I believe I have had built a strong base so the future students working on the project will since now on be able to isolate each small subsystem, work on them independently and bring a great number of improvements.