%!TEX root = ../Thesis.tex
\chapter{Acknowledgements}

I would like to thank my DTU's supervisor Nenad Mijatovic for giving me a lot of trust and understanding, so I could organise my working time in the most suitable way. There were many perturbations on the way and although stress and unlucky events, I have never been criticised or nag but rather admired for my work. This gave me the power to go through the moments where I doubted if my skills and expertise are up to the task.

In the final stage of work, I needed to move back to Korea, where I am writing these words right now. The need was not only dictated by KAIST graduation requirements but I believed that it would help me in finding motivation for writing. All my hopes were overfilled by Profesor Naehyuck Chang (KAIST's supervisor) who provided me with a great working environment and have been the first to review my this thesis. His opinion was valuable for me, he gave me hope and pointed further direction.

Of course, I would like to thank the whole team working on the car, I believe it was a great experience for us all. Here I would like to give special acknowledgement to Martin van der Bijl who kept me company during never-ending days in the laboratory, it was really nice to have someone to share my thoughts with time to time.

Moreover, I would like to thank my boss (to cover my expenses of living in aboard I needed to simultaneously work through the whole period of my master studies). I have been offered position when due to financial reasons I been considered dropping studies. I felt anxious as it was my first long-term job, however, I was given a lot of recognition and flexibility which made it possible for me to attend and complete this degree.

Last but not least I would like to thank my family for their never-ending mental support and never questioning my decisions. You are the root of each and every one of my little success.  